---
title: "Data Exploration"
author: "Ashlee Mikkelsen"
date: '`r Sys.Date()`'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

# Environment setup

## Work space

```{r}

rm(list = ls())

setwd("C:/Users/amikk/Documents/Rprojects/BrownBearDietThroughTime")

```


## Load packages

```{r}

library(ggplot2)
library(viridis)

```


## Graphing settings

```{r}

mytheme <- theme(
    axis.text = element_text(size = 12,face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    panel.grid.major = element_line(color = "grey92"),
    panel.grid.minor = element_line(color = "grey96"),
    panel.background = element_rect(fill = "white"),
    axis.line = element_line(colour = "black",linewidth = 1),
    axis.ticks = element_line(linewidth = 1),
    legend.position = "top"
    )
theme_set(mytheme)

P <- palette(viridis(40))
P <- palette(viridis(40))

```


## Laod data

```{r}
BearSI <- read.csv("BearStableIsotopes_Cleaned_Full.csv")
BearSI <- subset(BearSI, year>1994)

repro.annual.Dams <- read.csv("DfStats_ReproAnnual_Dams_clean.csv")
head(repro.annual.Dams)

repro.annual.Sfems <- read.csv("DfStats_ReproAnnual_Sfems_clean.csv")
head(repro.annual.Sfems)

repro.annual.Smales <- read.csv("DfStats_ReproAnnual_Smales_clean.csv")
head(repro.annual.Smales)



```


## Secondary data tables

```{r}

Protein.Sfems <- subset(repro.annual.Sfems, Source!="Bilberry")
Protein.Sfems <- subset(Protein.Sfems, Source!="Crowberry")
Protein.Sfems <- subset(Protein.Sfems, Source!="Lingonberry")
Protein.Sfems$Repro <- "Sfem"

Protein.Smales <- subset(repro.annual.Smales, Source!="Bilberry")
Protein.Smales <- subset(Protein.Smales, Source!="Crowberry")
Protein.Smales <- subset(Protein.Smales, Source!="Lingonberry")
Protein.Smales$Repro <- "Smale"

Protein.Dams <- subset(repro.annual.Dams, Source!="Bilberry")
Protein.Dams <- subset(Protein.Dams, Source!="Crowberry")
Protein.Dams <- subset(Protein.Dams, Source!="Lingonberry")
Protein.Dams$Repro <- "Dam"

Protein <- rbind.data.frame(Protein.Dams,
                            Protein.Sfems,
                            Protein.Smales)




```


# Data properties

```{r}
table(BearSI$BearID)
Bear.ID <- as.factor(BearSI$BearID)
Nbear <- nlevels(Bear.ID)
 min(BearSI$year)
 max(BearSI$year)
 2020-1992
 
 

```


We have 1160 observations from 512 different bears from 1992 to 2020 (28 years). We have many resamples (up to 13 times).

## Visualize data

```{r}

ggplot(data = BearSI, aes(year, N15))+
  geom_point(size=2,
             alpha=0.3)+
  geom_boxplot(aes(group=year, fill=year),
               alpha=0.4)+
  scale_fill_viridis()+
  xlab("Year")+
  ylab(expression(paste(delta^15,"N (\u2030)",sep = "")))+
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand=c(0.01,0.01),
                     breaks = seq(1995,2020,5))+
  theme(legend.position = "none")


ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="d15N_Year.pdf")
ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="d15N_Year.png")



```





```{r}


ggplot(data = BearSI, aes(year, C13.suess))+
  geom_point(size=2,
             alpha=0.3)+
  geom_boxplot(aes(group=year, fill=year),
               alpha=0.4)+
  scale_fill_viridis()+
  xlab("Year")+
  ylab(expression(paste(delta^13,"C (\u2030)",sep = "")))+
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand=c(0.01,0.01),
                     breaks = seq(1995,2020,5))+
  theme(legend.position = "none")

ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="d13C_Year.pdf")
ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="d13C_Year.png")


```

# Females with offspring

### Diet means across years- Dams

```{r}

ggplot(data = repro.annual.Dams,
       aes(Year,Mean, color=Source))+
  geom_line(aes(color=Source, group=Source),
            alpha=0.6)+
  geom_point(size=3,
             alpha=0.7)+
  scale_color_viridis(discrete = TRUE, end=0.95)+
  ylab("Estimated mean diet proportions for dams")+
  xlab("Year")+
  scale_x_discrete(expand = c(0,0),
                     breaks = seq(1995,2020,5))
  

ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="DamDietMean_Year.pdf")
ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="DamDietMean_Year.png")


```


# Single Females

### Diet means across years- Single Fems

```{r}

ggplot(data = repro.annual.Sfems,
       aes(Year,Mean, color=Source))+
  geom_line(aes(color=Source, group=Source),
            alpha=0.6)+
  geom_point(size=3,
             alpha=0.7,
             pch=17)+
  scale_color_viridis(discrete = TRUE, end=0.95)+
  ylab("Estimated mean diet proportions for solitary females")+
  xlab("Year")+
  scale_x_discrete(expand = c(0,0),
                     breaks = seq(1995,2020,5))
  

ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="SfemsDietMean_Year.pdf")
ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="SfemsDietMean_Year.png")


```



# Single Males

### Diet means across years- Single Males

```{r}

ggplot(data = repro.annual.Smales,
       aes(Year,Mean, color=Source))+
  geom_line(aes(color=Source, group=Source),
            alpha=0.6)+
  geom_point(size=3,
             alpha=0.7,
             pch=15)+
  scale_color_viridis(discrete = TRUE, end=0.95)+
  ylab("Estimated mean diet proportions for solitary males")+
  xlab("Year")+
  scale_x_discrete(expand = c(0,0),
                     breaks = seq(1995,2020,5))
  

ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="SmalesDietMean_Year.pdf")
ggsave(height = 6, width = 9,
       units = "in",
       dpi=900,
       file="SmalesDietMean_Year.png")


```