---
title: "Carbon_DietSources_Freq"
author: "Ashlee Mikkelsen"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Introduction

## Background


## Research objectives

## Specific hypotheses

# Environment

```{r}

rm(list=ls())

```

## Set Working Directory

```{r}

 setwd("C:/Users/amikk/Documents/Rprojects/BrownBearDietThroughTime")

```


## Load Packages

```{r}

library(ggplot2)
library(lme4)
library(viridis)
library(wiqid)
library(AICcmodavg)

```



## Graphing theme

```{r}

mytheme <- theme(
    axis.text = element_text(size = 10,face = "bold"),
    axis.title = element_text(size = 12, face = "bold"),
    panel.grid.major = element_line(color = "grey92"),
    panel.grid.minor = element_line(color = "grey96"),
    panel.background = element_rect(fill = "white"),
    axis.line = element_line(colour = "black",linewidth = 1),
    axis.ticks = element_line(linewidth = 1),
    legend.position = "top"
    )
theme_set(mytheme)

P <- palette(viridis(40))
P <- palette(viridis(40))


```


## Data

### Load Data

```{r}

SI_Diet <- read.csv("Data\\RawBearData_SI_Proteins.csv")

LastYr <- as.numeric(max(SI_Diet$year.represent))

SI_Diet$year.represent <- as.numeric(SI_Diet$year.represent)
SI_Diet$C13 <- as.numeric(SI_Diet$C13)

C13.suess <- SI_Diet$C13-(+0.022*(LastYr-SI_Diet$year.represent))
SI_Diet$C13.suess <- C13.suess

SI_Diet$fYEAR <- as.factor(SI_Diet$year.represent)
is.na(SI_Diet$C13)

SI_Diet <- subset(SI_Diet, C13!="NA")
SI_Diet <- subset(SI_Diet, reprostatus.represent!="NA")

SI_Diet <- subset(SI_Diet,age!="NA")

names(SI_Diet)[2] <- "Year"
names(SI_Diet)[6] <- "Repro"
names(SI_Diet)[9] <- "Mass"

SI_Diet_Mharv <- subset(SI_Diet, Moose_Harv!="NA")
SI_Diet_Mharv$Bilberry.Quad <- SI_Diet_Mharv$Bilberry^2
scratch <- SI_Diet_Mharv$Bilberry+0.000001
SI_Diet_Mharv$Bilberry.LN <- log(scratch)

SI_Diet_Mharv$Bilberry.Lag.Quad <- SI_Diet_Mharv$Bilberry_Lag^2
scratch <- SI_Diet_Mharv$Bilberry_Lag+0.000001
SI_Diet_Mharv$Bilberry.Lag.LN <- log(scratch)

SI_Diet_Mharv$Moose_Harv.Quad <- SI_Diet_Mharv$Moose_Harv^2
SI_Diet_Mharv$Moose_Obs.Quad <- SI_Diet_Mharv$Moose_Obs^2
SI_Diet_Mharv$Calves.Quad <- SI_Diet_Mharv$Calves^2

SI_Diet_Mharv$Moose_Harv.Lag.Quad <- SI_Diet_Mharv$Moose_Harv_Lag^2
SI_Diet_Mharv$Moose_Obs.Lag.Quad <- SI_Diet_Mharv$Moose_Obs_Lag^2
SI_Diet_Mharv$Calves.Lag.Quad <- SI_Diet_Mharv$Calves_Lag^2

SI_Diet_Mharv$Moose_Harv.LN <- log(SI_Diet_Mharv$Moose_Harv)
SI_Diet_Mharv$Moose_Obs.LN <- log(SI_Diet_Mharv$Moose_Obs)
SI_Diet_Mharv$Calves.LN <- log(SI_Diet_Mharv$Calves)

SI_Diet_Mharv$Moose_Harv.Lag.LN <- log(SI_Diet_Mharv$Moose_Harv_Lag)
SI_Diet_Mharv$Moose_Obs.Lag.LN <- log(SI_Diet_Mharv$Moose_Obs_Lag)
SI_Diet_Mharv$Calves.Lag.LN <- log(SI_Diet_Mharv$Calves_Lag)


```


### Standardize cont. variables

```{r}

SI_Diet_Mharv$Zyear <- standardize(SI_Diet_Mharv$Year)
SI_Diet_Mharv$ZC13 <- standardize(SI_Diet_Mharv$C13.suess)
SI_Diet_Mharv$Zmass <- standardize(SI_Diet_Mharv$Mass)
SI_Diet_Mharv$Zprop_ants <- standardize(SI_Diet_Mharv$Prop_Ants)
SI_Diet_Mharv$Zprop_moose <- standardize(SI_Diet_Mharv$Prop_Moose)
SI_Diet_Mharv$Zprop_bilb <- standardize(SI_Diet_Mharv$Prop_BilBerry)
SI_Diet_Mharv$Zharvest_moose <- standardize(SI_Diet_Mharv$Moose_Harv)
SI_Diet_Mharv$Zobs_moose <- standardize(SI_Diet_Mharv$Moose_Obs)
SI_Diet_Mharv$Zcalves <- standardize(SI_Diet_Mharv$Calves)
SI_Diet_Mharv$Zbilb <- standardize(SI_Diet_Mharv$Bilberry)
SI_Diet_Mharv$Zlingon <- standardize(SI_Diet_Mharv$Lingonberry)
SI_Diet_Mharv$Zbilb.quad <- standardize(SI_Diet_Mharv$Bilberry.Quad)
SI_Diet_Mharv$Zbilb.ln <- standardize(SI_Diet_Mharv$Bilberry.LN)
SI_Diet_Mharv$Zharvest_moose.quad <- standardize(SI_Diet_Mharv$Moose_Harv.Quad)
SI_Diet_Mharv$Zharvest_moose.ln <- standardize(SI_Diet_Mharv$Moose_Harv.LN)
SI_Diet_Mharv$Zobs_moose.quad <- standardize(SI_Diet_Mharv$Moose_Obs.Quad)
SI_Diet_Mharv$Zobs_moose.ln <- standardize(SI_Diet_Mharv$Moose_Obs.LN)
SI_Diet_Mharv$Zcalves.quad <- standardize(SI_Diet_Mharv$Calves.Quad)
SI_Diet_Mharv$Zcalves.ln <- standardize(SI_Diet_Mharv$Calves.LN)
SI_Diet_Mharv$Zage <- standardize(SI_Diet_Mharv$age)


SI_Diet_Mharv$Zharvest_moose_lag <-
  standardize(SI_Diet_Mharv$Moose_Harv_Lag)
SI_Diet_Mharv$Zobs_moose_lag <- 
  standardize(SI_Diet_Mharv$Moose_Obs_Lag)
SI_Diet_Mharv$Zcalves_lag <- 
  standardize(SI_Diet_Mharv$Calves_Lag)
SI_Diet_Mharv$Zbilb_lag <-
  standardize(SI_Diet_Mharv$Bilberry_Lag)
SI_Diet_Mharv$Zlingon_lag <-
  standardize(SI_Diet_Mharv$Lingonberry_Lag)
SI_Diet_Mharv$Zbilb.quad_lag <-
  standardize(SI_Diet_Mharv$Bilberry.Lag.Quad)
SI_Diet_Mharv$Zbilb.ln_lag <- 
  standardize(SI_Diet_Mharv$Bilberry.Lag.LN)
SI_Diet_Mharv$Zharvest_moose.quad_lag <-
  standardize(SI_Diet_Mharv$Moose_Harv.Lag.Quad)
SI_Diet_Mharv$Zharvest_moose.ln_lag <-
  standardize(SI_Diet_Mharv$Moose_Harv.Lag.LN)
SI_Diet_Mharv$Zobs_moose.quad_lag <-
  standardize(SI_Diet_Mharv$Moose_Obs.Lag.Quad)
SI_Diet_Mharv$Zobs_moose.ln_lag <- 
  standardize(SI_Diet_Mharv$Moose_Obs.Lag.LN)
SI_Diet_Mharv$Zcalves.quad_lag <-
  standardize(SI_Diet_Mharv$Calves.Lag.Quad)
SI_Diet_Mharv$Zcalves.ln_lag <-
  standardize(SI_Diet_Mharv$Calves.Lag.LN)
SI_Diet_Mharv$Zcalves_lag <- 
  standardize(SI_Diet_Mharv$Calves_Lag)


```


# Data distributions


```{r}


ggplot(data = SI_Diet, aes(C13.suess))+
  geom_histogram(binwidth = sd(SI_Diet$C13.suess))+
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand = c(0,0))+
  xlab(expression(paste(delta^13,"C (\u2030)",sep = "")))

ggplot(data = SI_Diet, aes(C13.suess))+
  geom_histogram(binwidth = sd(SI_Diet$C13.suess),
                 aes(fill=fYEAR))+
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand = c(0,0))+
  xlab(expression(paste(delta^13,"C (\u2030)",sep = "")))+
  scale_fill_viridis(discrete = TRUE,
                     option="B")

Annual_d13C_plot <- ggplot(data = SI_Diet, aes(Year, C13.suess))+
  geom_jitter(aes(color=Repro),
             alpha=0.4,
             width = 0.1)+
  geom_boxplot(aes(group=Year),
               alpha=0.2)+
  scale_color_viridis(discrete = TRUE, end = 0.95)+
  scale_y_continuous(expand = c(0.01,0.01))+
  scale_x_continuous(expand = c(0.01,0.01))+
  ylab(expression(paste(delta^13,"C (\u2030)",sep = "")))+
  labs(color="Reproductive catergory")


ggsave(plot = Annual_d13C_plot,
       "Annual_d13C_plot.png",
       height = 4.5,width = 6.5,
       units="in",
       dpi=700)


```



# Linear regression models

## Model Selection setup

```{r}

CarbonModels <- list()


```


### Intercept model

```{r}

CarbonModels[[1]] <- IntMod <- lmer(ZC13~1+(1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(IntMod)
AIcc_Int <- wiqid::AICc(IntMod)

```


### Year model

```{r}

CarbonModels[[2]] <-YearMod <- lmer(ZC13~Zyear+(1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(YearMod)
AIcc_Year <- wiqid::AICc(YearMod)

```


### Ants model

```{r}

AntMod <- lmer(ZC13~ Zprop_ants+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(AntMod)

AIcc_Ant <- wiqid::AICc(AntMod)

```


### Moose diet model

```{r}

MooseDietMod <- lmer(ZC13~ Zprop_moose+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(MooseDietMod)

AIcc_DietMoose <- wiqid::AICc(MooseDietMod)

```


### Moose harvest models


```{r}


ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Moose_Harv),
            linewidth=1,
            color=P[20])

ggplot(data = SI_Diet_Mharv)+
   geom_line(aes(Year, Moose_Harv.Quad),
            linewidth=1,
            color=P[23],
            linetype="dashed")

ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Moose_Harv.LN),
            linewidth=1,
            color=P[26],
            linetype="dotdash")


```


```{r}

MooseHarvMods <- list()

MooseHarvMods[[1]] <-
  Lin.MooseHarvMod <- 
  lmer(ZC13~ Zharvest_moose+
             (1|BearID)+(1|Repro),
            data = SI_Diet_Mharv) 
summary(Lin.MooseHarvMod)
AIcc_HarvMoose.Lin <- wiqid::AICc(Lin.MooseHarvMod)

MooseHarvMods[[2]] <-
  Log.MooseHarvMod <-
  lmer(ZC13~ Zharvest_moose.ln+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv) 
summary(Log.MooseHarvMod)
AIcc_HarvMoose.Log <- wiqid::AICc(Log.MooseHarvMod)


MooseHarvMods[[3]] <-
  Quad.MooseHarvMod <- 
  lmer(ZC13~ Zharvest_moose+
  Zharvest_moose.quad+
  (1|BearID)+(1|Repro),
data = SI_Diet_Mharv)

summary(Quad.MooseHarvMod)
AIcc_HarvMoose.Quad <- wiqid::AICc(Quad.MooseHarvMod)


CarbonModels[[3]] <-MooseHarvMod <- Lin.MooseHarvMod
  
```


### Calf observation models

```{r}

ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Calves))+
  scale_x_continuous(expand = c(0,0))

CalfMods <- list()

CalfMods[[1]] <-Lin.CalfMod <- lmer(ZC13~ Zcalves+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv) 
summary(Lin.CalfMod)
AIcc_Calf.Lin <- wiqid::AICc(Lin.CalfMod)

CalfMods[[2]] <-Log.CalfMod <- 
  lmer(ZC13~ Zcalves.ln+
      (1|BearID)+(1|Repro),
      data = SI_Diet_Mharv) 
summary(Log.CalfMod)
AIcc_Calf.Log <- wiqid::AICc(Log.CalfMod)


CalfMods[[3]] <-
  Quad.CalfMod <-
  lmer(ZC13~Zcalves+
      Zcalves.quad+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv)

summary(Quad.CalfMod)
AIcc_Calf.Quad <- wiqid::AICc(Quad.CalfMod)



CarbonModels[[4]] <-
  CalfMod <-Lin.CalfMod

```



### Moose observation models

```{r}

MooseObsMods <- list()

MooseObsMods[[1]] <-
  Lin.MooseObsMod <- 
  lmer(ZC13~ Zobs_moose+
  (1|BearID)+(1|Repro),
data = SI_Diet_Mharv) 

summary(Lin.MooseObsMod)
AIcc_MooseObs.Lin <- wiqid::AICc(Lin.MooseObsMod)

MooseObsMods[[2]] <-
  Log.MooseObsMod <- 
  lmer(ZC13~ Zobs_moose.ln+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv) 
summary(Log.MooseObsMod)
AIcc_MooseObs.Log <- wiqid::AICc(Log.MooseObsMod)


MooseObsMods[[3]] <-
  Quad.MooseObsMod <-
  lmer(ZC13~Zobs_moose+
      Zobs_moose.quad+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv)

summary(Quad.MooseObsMod)
AIcc_MooseObs.Quad <- wiqid::AICc(Quad.MooseObsMod)

CarbonModels[[5]] <-
  MooseObsMod <- 
  Log.MooseObsMod

```



### Bilberry models


```{r}

ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Bilberry),
            linewidth=1,
            color=P[5])+
   geom_line(aes(Year, Bilberry.Quad),
            linewidth=1,
            color=P[8],
            linetype="dashed")+
  geom_line(aes(Year, Bilberry.LN),
            linewidth=1,
            color=P[11],
            linetype="dotdash")


```



```{r}

BilbModels <- list()

BilbModels[[1]] <-LinBilbMod <- lmer(ZC13~ Zbilb+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

AIcc_Bilb.Lin <- wiqid::AICc(LinBilbMod)

BilbModels[[2]] <-QuadBilbMod <- lmer(ZC13~ Zbilb+Zbilb.quad+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)


AIcc_Bilb.Quad <- wiqid::AICc(QuadBilbMod)

BilbModels[[3]] <-LogBilbMod <- lmer(ZC13~ Zbilb.ln+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(LogBilbMod)


AIcc_Bilb.Log <- wiqid::AICc(LogBilbMod)


```




```{r}

CarbonModels[[6]] <-BilbMod <- LogBilbMod


```


### Lingonberry model

```{r}
LingTest <- subset(SI_Diet_Mharv, Lingonberry!="")

LT.int <-
  lmer(ZC13~ 1+
         (1|BearID)+(1|Repro),
       data = LingTest)
LT.AIC.Int <- wiqid::AICc(LT.int)

LT.ling <- 
  lmer(ZC13~ Zlingon+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)
LT.AIC.Ling <- wiqid::AICc(LT.ling)


ggplot(data =SI_Diet_Mharv, aes(Year, Lingonberry))+
  geom_line()



```

### Age model

```{r}

CarbonModels[[7]] <-AgeMod <- lmer(ZC13~ Zage+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(AgeMod)

AIcc_Age <- wiqid::AICc(AgeMod)



```


## Time lagged models

During one of our discusssions of this analysis, Anne brought up the complexity of the timeline within our system. Initially, I considered the associations between berries and moose on the landscape that are reorted fro the year that hair was grown. However, there may be carry-over affects from diet the previous year, or an abundance of moose carcasses in the fall from the harvest the previous fall and winter, thus the moose value from the year prior to hair growth may be more relevant than moose during the year of moose growth.

Therefore, I created a secondary set of landscape variables that have a 1-year lag, meaning that hair grown in 2006 is associated with moose and berry production from 2005, rather than 2006.

```{r}

SI_Diet_Tlag <- subset(SI_Diet_Mharv, Moose_Harv_Lag!="")

TLModels <- list()

TLModels[[1]] <- TimeLag.Int <-
  lmer(ZC13~ 1+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag) 

AIcc_TL_int <- wiqid::AICc(TimeLag.Int)


```


### Lagged Moose harvest

```{r}

MooseHarvMods.Lagged <- list()

MooseHarvMods.Lagged[[1]] <-
  Lin.MooseHarvMod.Lag <- 
  lmer(ZC13~ Zharvest_moose_lag+
             (1|BearID)+(1|Repro),
            data = SI_Diet_Tlag) 
summary(Lin.MooseHarvMod.Lag)
AIcc_HarvMoose.Lin.Lag <- wiqid::AICc(Lin.MooseHarvMod.Lag)

MooseHarvMods.Lagged[[2]] <-
  Log.MooseHarvMod.Lag <-
  lmer(ZC13~ Zharvest_moose.ln_lag+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag) 
summary(Log.MooseHarvMod.Lag)
AIcc_HarvMoose.Log.Lag <- wiqid::AICc(Log.MooseHarvMod.Lag)


MooseHarvMods.Lagged[[3]] <-
   Quad.MooseHarvMod.Lag  <- 
  lmer(ZC13~ Zharvest_moose_lag+
  Zharvest_moose.quad_lag+
  (1|BearID)+(1|Repro),
data = SI_Diet_Tlag)

summary(Quad.MooseHarvMod.Lag)
AIcc_HarvMoose.Quad.Lag <- wiqid::AICc(Quad.MooseHarvMod.Lag)

print(AIcc_HarvMoose.Lin.Lag)
print(AIcc_HarvMoose.Log.Lag)
print(AIcc_HarvMoose.Quad.Lag)

summary(Quad.MooseHarvMod.Lag)

TLModels[[2]] <- Log.MooseHarvMod.Lag


```


### Lagged Moose Calves

```{r}


CalfMods.lag <- list()

CalfMods.lag [[1]] <-Lin.CalfMod.Lag <-
  lmer(ZC13~ Zcalves+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Tlag) 
summary(Lin.CalfMod.Lag)
AIcc_Calf.Lin.Lag <- wiqid::AICc(Lin.CalfMod.Lag)

CalfMods.lag [[2]] <-Log.CalfMod.Lag <- 
  lmer(ZC13~ Zcalves.ln_lag+
      (1|BearID)+(1|Repro),
      data = SI_Diet_Mharv) 
summary(Log.CalfMod.Lag)
AIcc_Calf.Log.Lag <- wiqid::AICc(Log.CalfMod.Lag)


CalfMods.lag[[3]] <-
  Quad.CalfMod.Lag <-
  lmer(ZC13~Zcalves+
      Zcalves.quad+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag)

summary(Quad.CalfMod.Lag)
AIcc_Calf.Quad.lag <- wiqid::AICc(Quad.CalfMod.Lag)

print(AIcc_Calf.Lin.Lag)
print(AIcc_Calf.Log.Lag)
print(AIcc_Calf.Quad.lag)



TLModels[[3]] <-
  Lin.CalfMod.Lag 


```


### Lagged Moose Observation 

```{r}

MooseObsMods.Lag <- list()

MooseObsMods.Lag[[1]] <-
  Lin.MooseObsMod.Lag <- 
  lmer(ZC13~ Zobs_moose_lag+
  (1|BearID)+(1|Repro),
data = SI_Diet_Tlag) 

summary(Lin.MooseObsMod.Lag)
AIcc_MooseObs.Lin.Lag <- wiqid::AICc(Lin.MooseObsMod.Lag)

MooseObsMods.Lag[[2]] <-
  Log.MooseObsMod.Lag <- 
  lmer(ZC13~ Zobs_moose.ln_lag+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag) 
summary(Log.MooseObsMod.Lag)
AIcc_MooseObs.Log.Lag <- wiqid::AICc(Log.MooseObsMod.Lag)


MooseObsMods.Lag[[3]] <-
  Quad.MooseObsMod.Lag <-
  lmer(ZC13~Zobs_moose_lag+
      Zobs_moose.quad_lag+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag)

summary(Quad.MooseObsMod.Lag)
AIcc_MooseObs.Quad.Lag <- wiqid::AICc(Quad.MooseObsMod.Lag)

print(AIcc_MooseObs.Lin.Lag)
print(AIcc_MooseObs.Log.Lag)
print(AIcc_MooseObs.Quad.Lag)
summary(Log.MooseObsMod.Lag)

TLModels[[4]] <-  Log.MooseObsMod.Lag

```



### Lagged Bilberry models


```{r}

BilbModels.Lag <- list()

BilbModels.Lag[[1]] <-LinBilbMod.Lag <-
  lmer(ZC13~ Zbilb_lag+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)

AIcc_Bilb.Lin.Lag <- wiqid::AICc(LinBilbMod.Lag)

BilbModels.Lag[[2]] <-QuadBilbMod.Lag <- 
  lmer(ZC13~ Zbilb_lag+Zbilb.quad_lag+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)

AIcc_Bilb.Quad.Lag <- wiqid::AICc(QuadBilbMod.Lag)


BilbModels.Lag[[3]] <-
  LogBilbMod.Lag <-
  lmer(ZC13~ Zbilb.ln_lag+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)


AIcc_Bilb.Log.Lag <- wiqid::AICc(LogBilbMod.Lag)

print(AIcc_Bilb.Lin.Lag)
print(AIcc_Bilb.Log.Lag)
print(AIcc_Bilb.Quad.Lag)

summary(LinBilbMod.Lag)


TLModels[[5]] <-  LinBilbMod.Lag


```


### Lagged age model


```{r}

TLModels[[6]] <-  
  AgeMod.Lag <- 
  lmer(ZC13~ Zage+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)

summary(AgeMod.Lag)
AIcc_AgeLag <- wiqid::AICc(AgeMod.Lag)


```



## Model selection table

### year-year models

```{r}

CarbonModelNames <- c("Intercept",
                     "Year",
                     "Moose Harvest",
                     "Calf Observation",
                     "Moose Observation",
                     "Bilberry Index",
                     "Age")

##Generate and print AICc table
print(aictab(cand.set = CarbonModels,
             modnames = CarbonModelNames,
             sort = TRUE),
      digits = 4, #round to 4 digits after decimal point
      LL = TRUE #give log-likelihood 
      )

write.csv(aictab(cand.set = CarbonModels,
                 modnames = CarbonModelNames,
                 sort = TRUE,
                 second.ord=TRUE),
          file="Results\\CarbonModels.csv")



```


### time-lagged models

```{r}

TLModelNames <- c("Intercept",
                  "Lagged Moose Harvest",
                  "Lagged Calf Observation",
                  "Lagged Moose Observation",
                  "Lagged Bilberry Index",
                  "Age")

##Generate and print AICc table
print(aictab(cand.set = TLModels,
             modnames = TLModelNames,
             sort = TRUE),
      digits = 4, #round to 4 digits after decimal point
      LL = TRUE #give log-likelihood 
      )

write.csv(aictab(cand.set = TLModels,
                 modnames = TLModelNames,
                 sort = TRUE,
                 second.ord=TRUE),
          file="Results\\Carbon_TimeLagModels.csv")

ggplot(data = SI_Diet_Tlag, aes(age,C13.suess))+
  geom_jitter(width = 0.2,
              alpha=0.6,
              aes(color=Repro))+
  scale_color_viridis(option="B",
                      discrete = TRUE,
                      end=0.8)

```



# Results

