---
title: "Carbon_DietSources_Freq"
author: "Ashlee Mikkelsen"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Introduction

## Background


## Research objectives

## Specific hypotheses

# Environment

```{r}

rm(list=ls())

```

## Set Working Directory

```{r}

 setwd("C:/Users/amikk/Documents/Rprojects/BrownBearDietThroughTime")

```


## Load Packages

```{r}

library(ggplot2)
library(lme4)
library(viridis)
library(wiqid)
library(AICcmodavg)
library(ggExtra)
library(ggiraphExtra)
library(ggeffects)
library(gridExtra)
library(rphylopic)


```



## Graphing theme

```{r}

moose.img <- pick_phylopic(name = "Alces alces")
bilb.img <- pick_phylopic(name = "Vaccinium")

mytheme <- theme(
    axis.text = element_text(size = 10,face = "bold"),
    axis.title = element_text(size = 12, face = "bold"),
    panel.grid.major = element_line(color = "grey92"),
    panel.grid.minor = element_line(color = "grey96"),
    panel.background = element_rect(fill = "white"),
    axis.line = element_line(colour = "black",linewidth = 1),
    axis.ticks = element_line(linewidth = 1),
    legend.position = "top"
    )
theme_set(mytheme)

P <- palette(viridis(40))
P <- palette(viridis(40))


```


## Data

### Load Data

```{r}

SI_Diet <- read.csv("Data\\RawBearData_SI_Proteins.csv")

LastYr <- as.numeric(max(SI_Diet$year.represent))

SI_Diet$year.represent <- as.numeric(SI_Diet$year.represent)
SI_Diet$C13 <- as.numeric(SI_Diet$C13)

C13.suess <- SI_Diet$C13-(+0.022*(LastYr-SI_Diet$year.represent))
SI_Diet$C13.suess <- C13.suess

SI_Diet$fYEAR <- as.factor(SI_Diet$year.represent)
is.na(SI_Diet$C13)

SI_Diet <- subset(SI_Diet, C13.suess!="NA")
SI_Diet <- subset(SI_Diet, reprostatus.represent!="NA")
SI_Diet <- subset(SI_Diet,age!="NA")
SI_Diet <- subset(SI_Diet, age<20)


names(SI_Diet)[2] <- "Year"
names(SI_Diet)[6] <- "Repro"
names(SI_Diet)[9] <- "Mass"

SI_Diet_Mharv <- subset(SI_Diet, Moose_Harv!="NA")
SI_Diet_Mharv$Bilberry.Quad <- SI_Diet_Mharv$Bilberry^2
scratch <- SI_Diet_Mharv$Bilberry+0.000001
SI_Diet_Mharv$Bilberry.LN <- log(scratch)

SI_Diet_Mharv$Bilberry.Lag.Quad <- SI_Diet_Mharv$Bilberry_Lag^2
scratch <- SI_Diet_Mharv$Bilberry_Lag+0.000001
SI_Diet_Mharv$Bilberry.Lag.LN <- log(scratch)

SI_Diet_Mharv$Moose_Harv.Quad <- SI_Diet_Mharv$Moose_Harv^2
SI_Diet_Mharv$Moose_Obs.Quad <- SI_Diet_Mharv$Moose_Obs^2
SI_Diet_Mharv$Calves.Quad <- SI_Diet_Mharv$Calves^2

SI_Diet_Mharv$Moose_Harv.Lag.Quad <- SI_Diet_Mharv$Moose_Harv_Lag^2
SI_Diet_Mharv$Moose_Obs.Lag.Quad <- SI_Diet_Mharv$Moose_Obs_Lag^2
SI_Diet_Mharv$Calves.Lag.Quad <- SI_Diet_Mharv$Calves_Lag^2

SI_Diet_Mharv$Moose_Harv.LN <- log(SI_Diet_Mharv$Moose_Harv)
SI_Diet_Mharv$Moose_Obs.LN <- log(SI_Diet_Mharv$Moose_Obs)
SI_Diet_Mharv$Calves.LN <- log(SI_Diet_Mharv$Calves)

SI_Diet_Mharv$Moose_Harv.Lag.LN <- log(SI_Diet_Mharv$Moose_Harv_Lag)
SI_Diet_Mharv$Moose_Obs.Lag.LN <- log(SI_Diet_Mharv$Moose_Obs_Lag)
SI_Diet_Mharv$Calves.Lag.LN <- log(SI_Diet_Mharv$Calves_Lag)


```


### Standardize cont. variables

```{r}

SI_Diet_Mharv$Zyear <- standardize(SI_Diet_Mharv$Year)
SI_Diet_Mharv$ZC13 <- standardize(SI_Diet_Mharv$C13.suess)
SI_Diet_Mharv$Zmass <- standardize(SI_Diet_Mharv$Mass)
SI_Diet_Mharv$Zprop_ants <- standardize(SI_Diet_Mharv$Prop_Ants)
SI_Diet_Mharv$Zprop_moose <- standardize(SI_Diet_Mharv$Prop_Moose)
SI_Diet_Mharv$Zprop_bilb <- standardize(SI_Diet_Mharv$Prop_BilBerry)
SI_Diet_Mharv$Zharvest_moose <- standardize(SI_Diet_Mharv$Moose_Harv)
SI_Diet_Mharv$Zobs_moose <- standardize(SI_Diet_Mharv$Moose_Obs)
SI_Diet_Mharv$Zcalves <- standardize(SI_Diet_Mharv$Calves)
SI_Diet_Mharv$Zbilb <- standardize(SI_Diet_Mharv$Bilberry)
SI_Diet_Mharv$Zlingon <- standardize(SI_Diet_Mharv$Lingonberry)
SI_Diet_Mharv$Zbilb.quad <- standardize(SI_Diet_Mharv$Bilberry.Quad)
SI_Diet_Mharv$Zbilb.ln <- standardize(SI_Diet_Mharv$Bilberry.LN)
SI_Diet_Mharv$Zharvest_moose.quad <- standardize(SI_Diet_Mharv$Moose_Harv.Quad)
SI_Diet_Mharv$Zharvest_moose.ln <- standardize(SI_Diet_Mharv$Moose_Harv.LN)
SI_Diet_Mharv$Zobs_moose.quad <- standardize(SI_Diet_Mharv$Moose_Obs.Quad)
SI_Diet_Mharv$Zobs_moose.ln <- standardize(SI_Diet_Mharv$Moose_Obs.LN)
SI_Diet_Mharv$Zcalves.quad <- standardize(SI_Diet_Mharv$Calves.Quad)
SI_Diet_Mharv$Zcalves.ln <- standardize(SI_Diet_Mharv$Calves.LN)
SI_Diet_Mharv$Zage <- standardize(SI_Diet_Mharv$age)


SI_Diet_Mharv$Zharvest_moose_lag <-
  standardize(SI_Diet_Mharv$Moose_Harv_Lag)
SI_Diet_Mharv$Zobs_moose_lag <- 
  standardize(SI_Diet_Mharv$Moose_Obs_Lag)
SI_Diet_Mharv$Zcalves_lag <- 
  standardize(SI_Diet_Mharv$Calves_Lag)
SI_Diet_Mharv$Zbilb_lag <-
  standardize(SI_Diet_Mharv$Bilberry_Lag)
SI_Diet_Mharv$Zlingon_lag <-
  standardize(SI_Diet_Mharv$Lingonberry_Lag)
SI_Diet_Mharv$Zbilb.quad_lag <-
  standardize(SI_Diet_Mharv$Bilberry.Lag.Quad)
SI_Diet_Mharv$Zbilb.ln_lag <- 
  standardize(SI_Diet_Mharv$Bilberry.Lag.LN)
SI_Diet_Mharv$Zharvest_moose.quad_lag <-
  standardize(SI_Diet_Mharv$Moose_Harv.Lag.Quad)
SI_Diet_Mharv$Zharvest_moose.ln_lag <-
  standardize(SI_Diet_Mharv$Moose_Harv.Lag.LN)
SI_Diet_Mharv$Zobs_moose.quad_lag <-
  standardize(SI_Diet_Mharv$Moose_Obs.Lag.Quad)
SI_Diet_Mharv$Zobs_moose.ln_lag <- 
  standardize(SI_Diet_Mharv$Moose_Obs.Lag.LN)
SI_Diet_Mharv$Zcalves.quad_lag <-
  standardize(SI_Diet_Mharv$Calves.Lag.Quad)
SI_Diet_Mharv$Zcalves.ln_lag <-
  standardize(SI_Diet_Mharv$Calves.Lag.LN)
SI_Diet_Mharv$Zcalves_lag <- 
  standardize(SI_Diet_Mharv$Calves_Lag)


```


# Data distributions


```{r}


ggplot(data = SI_Diet, aes(C13.suess))+
  geom_histogram(binwidth = sd(SI_Diet$C13.suess))+
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand = c(0,0))+
  xlab(expression(paste(delta^13,"C (\u2030)",sep = "")))

ggplot(data = SI_Diet, aes(C13.suess))+
  geom_histogram(binwidth = sd(SI_Diet$C13.suess),
                 aes(fill=fYEAR))+
  scale_y_continuous(expand = c(0,0))+
  scale_x_continuous(expand = c(0,0))+
  xlab(expression(paste(delta^13,"C (\u2030)",sep = "")))+
  scale_fill_viridis(discrete = TRUE,
                     option="B")

Annual_d13C_plot <- ggplot(data = SI_Diet, aes(Year, C13.suess))+
  geom_jitter(aes(color=Repro),
             alpha=0.4,
             width = 0.1)+
  geom_boxplot(aes(group=Year),
               alpha=0.2)+
  scale_color_viridis(discrete = TRUE, end = 0.95)+
  scale_y_continuous(expand = c(0.01,0.01))+
  scale_x_continuous(expand = c(0.01,0.01))+
  ylab(expression(paste(delta^13,"C (\u2030)",sep = "")))+
  labs(color="Reproductive catergory")


ggsave(plot = Annual_d13C_plot,
       "Annual_d13C_plot.png",
       height = 4.5,width = 6.5,
       units="in",
       dpi=700)


```



# Linear regression models

## Model Selection setup

```{r}

CarbonModels <- list()


```


### Intercept model

```{r}

CarbonModels[[1]] <- IntMod <- lmer(ZC13~1+(1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(IntMod)
AIcc_Int <- wiqid::AICc(IntMod)

```


### Year model

```{r}

CarbonModels[[2]] <-YearMod <- lmer(ZC13~Zyear+(1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(YearMod)
AIcc_Year <- wiqid::AICc(YearMod)

```


### Ants model

```{r}

AntMod <- lmer(ZC13~ Zprop_ants+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(AntMod)

AIcc_Ant <- wiqid::AICc(AntMod)

```


### Moose diet model

```{r}

MooseDietMod <- lmer(ZC13~ Zprop_moose+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(MooseDietMod)

AIcc_DietMoose <- wiqid::AICc(MooseDietMod)

```


### Moose harvest models


```{r}


ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Moose_Harv),
            linewidth=1,
            color=P[20])

ggplot(data = SI_Diet_Mharv)+
   geom_line(aes(Year, Moose_Harv.Quad),
            linewidth=1,
            color=P[23],
            linetype="dashed")

ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Moose_Harv.LN),
            linewidth=1,
            color=P[26],
            linetype="dotdash")


```


```{r}

MooseHarvMods <- list()

MooseHarvMods[[1]] <-
  Lin.MooseHarvMod <- 
  lmer(ZC13~ Zharvest_moose+
             (1|BearID)+(1|Repro),
            data = SI_Diet_Mharv) 
summary(Lin.MooseHarvMod)
AIcc_HarvMoose.Lin <- wiqid::AICc(Lin.MooseHarvMod)

MooseHarvMods[[2]] <-
  Log.MooseHarvMod <-
  lmer(ZC13~ Zharvest_moose.ln+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv) 
summary(Log.MooseHarvMod)
AIcc_HarvMoose.Log <- wiqid::AICc(Log.MooseHarvMod)


MooseHarvMods[[3]] <-
  Quad.MooseHarvMod <- 
  lmer(ZC13~ Zharvest_moose+
  Zharvest_moose.quad+
  (1|BearID)+(1|Repro),
data = SI_Diet_Mharv)

summary(Quad.MooseHarvMod)
AIcc_HarvMoose.Quad <- wiqid::AICc(Quad.MooseHarvMod)


CarbonModels[[3]] <-MooseHarvMod <- Lin.MooseHarvMod
  
```


### Calf observation models

```{r}

ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Calves))+
  scale_x_continuous(expand = c(0,0))

CalfMods <- list()

CalfMods[[1]] <-Lin.CalfMod <- lmer(ZC13~ Zcalves+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv) 
summary(Lin.CalfMod)
AIcc_Calf.Lin <- wiqid::AICc(Lin.CalfMod)

CalfMods[[2]] <-Log.CalfMod <- 
  lmer(ZC13~ Zcalves.ln+
      (1|BearID)+(1|Repro),
      data = SI_Diet_Mharv) 
summary(Log.CalfMod)
AIcc_Calf.Log <- wiqid::AICc(Log.CalfMod)


CalfMods[[3]] <-
  Quad.CalfMod <-
  lmer(ZC13~Zcalves+
      Zcalves.quad+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv)



CarbonModels[[4]] <-
  CalfMod <-Lin.CalfMod

```



### Moose observation models

```{r}

MooseObsMods <- list()

MooseObsMods[[1]] <-
  Lin.MooseObsMod <- 
  lmer(ZC13~ Zobs_moose+
  (1|BearID)+(1|Repro),
data = SI_Diet_Mharv) 

summary(Lin.MooseObsMod)
AIcc_MooseObs.Lin <- wiqid::AICc(Lin.MooseObsMod)

MooseObsMods[[2]] <-
  Log.MooseObsMod <- 
  lmer(ZC13~ Zobs_moose.ln+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv) 
summary(Log.MooseObsMod)
AIcc_MooseObs.Log <- wiqid::AICc(Log.MooseObsMod)


MooseObsMods[[3]] <-
  Quad.MooseObsMod <-
  lmer(ZC13~Zobs_moose+
      Zobs_moose.quad+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Mharv)

summary(Quad.MooseObsMod)
AIcc_MooseObs.Quad <- wiqid::AICc(Quad.MooseObsMod)

CarbonModels[[5]] <-
  MooseObsMod <- 
  Log.MooseObsMod

```



### Bilberry models


```{r}

ggplot(data = SI_Diet_Mharv)+
  geom_line(aes(Year, Bilberry),
            linewidth=1,
            color=P[5])+
   geom_line(aes(Year, Bilberry.Quad),
            linewidth=1,
            color=P[8],
            linetype="dashed")+
  geom_line(aes(Year, Bilberry.LN),
            linewidth=1,
            color=P[11],
            linetype="dotdash")


```



```{r}

BilbModels <- list()

BilbModels[[1]] <-LinBilbMod <- lmer(ZC13~ Zbilb+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

AIcc_Bilb.Lin <- wiqid::AICc(LinBilbMod)

BilbModels[[2]] <-QuadBilbMod <- lmer(ZC13~ Zbilb+Zbilb.quad+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)


AIcc_Bilb.Quad <- wiqid::AICc(QuadBilbMod)

BilbModels[[3]] <-LogBilbMod <- lmer(ZC13~ Zbilb.ln+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(LogBilbMod)


AIcc_Bilb.Log <- wiqid::AICc(LogBilbMod)


```




```{r}

CarbonModels[[6]] <-BilbMod <- LogBilbMod


```


### Age model

```{r}

CarbonModels[[7]] <-AgeMod <- lmer(ZC13~ Zage+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Mharv)

summary(AgeMod)

AIcc_Age <- wiqid::AICc(AgeMod)



```



### Moose and Bilb

```{r}


CarbonModels[[8]] <-
  LogBilbCalfMod <- 
  lmer(ZC13~ Zbilb.ln+
         Zcalves+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Mharv)

AIcc_BilbCalf <- AICc(LogBilbCalfMod)
summary(LogBilbCalfMod)

```



## Time lagged models

During one of our discusssions of this analysis, Anne brought up the complexity of the timeline within our system. Initially, I considered the associations between berries and moose on the landscape that are reorted fro the year that hair was grown. However, there may be carry-over affects from diet the previous year, or an abundance of moose carcasses in the fall from the harvest the previous fall and winter, thus the moose value from the year prior to hair growth may be more relevant than moose during the year of moose growth.

Therefore, I created a secondary set of landscape variables that have a 1-year lag, meaning that hair grown in 2006 is associated with moose and berry production from 2005, rather than 2006.

```{r}

SI_Diet_Tlag <- subset(SI_Diet_Mharv, Moose_Harv_Lag!="")

TLModels <- list()

TLModels[[1]] <- TimeLag.Int <-
  lmer(ZC13~ 1+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag) 

AIcc_TL_int <- wiqid::AICc(TimeLag.Int)


```


### Lagged Moose harvest

```{r}

MooseHarvMods.Lagged <- list()

MooseHarvMods.Lagged[[1]] <-
  Lin.MooseHarvMod.Lag <- 
  lmer(ZC13~ Zharvest_moose_lag+
             (1|BearID)+(1|Repro),
            data = SI_Diet_Tlag) 
summary(Lin.MooseHarvMod.Lag)
AIcc_HarvMoose.Lin.Lag <- wiqid::AICc(Lin.MooseHarvMod.Lag)

MooseHarvMods.Lagged[[2]] <-
  Log.MooseHarvMod.Lag <-
  lmer(ZC13~ Zharvest_moose.ln_lag+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag) 
summary(Log.MooseHarvMod.Lag)
AIcc_HarvMoose.Log.Lag <- wiqid::AICc(Log.MooseHarvMod.Lag)


MooseHarvMods.Lagged[[3]] <-
   Quad.MooseHarvMod.Lag  <- 
  lmer(ZC13~ Zharvest_moose_lag+
  Zharvest_moose.quad_lag+
  (1|BearID)+(1|Repro),
data = SI_Diet_Tlag)

summary(Quad.MooseHarvMod.Lag)
AIcc_HarvMoose.Quad.Lag <- wiqid::AICc(Quad.MooseHarvMod.Lag)

print(AIcc_HarvMoose.Lin.Lag)
print(AIcc_HarvMoose.Log.Lag)
print(AIcc_HarvMoose.Quad.Lag)

summary(Quad.MooseHarvMod.Lag)

TLModels[[2]] <- Lin.MooseHarvMod.Lag


```


### Lagged Moose Calves

```{r}


CalfMods.lag <- list()

CalfMods.lag [[1]] <-Lin.CalfMod.Lag <-
  lmer(ZC13~ Zcalves_lag+
                  (1|BearID)+(1|Repro),
                data = SI_Diet_Tlag) 
summary(Lin.CalfMod.Lag)
AIcc_Calf.Lin.Lag <- wiqid::AICc(Lin.CalfMod.Lag)

CalfMods.lag [[2]] <-Log.CalfMod.Lag <- 
  lmer(ZC13~ Zcalves.ln_lag+
      (1|BearID)+(1|Repro),
      data = SI_Diet_Mharv) 
summary(Log.CalfMod.Lag)
AIcc_Calf.Log.Lag <- wiqid::AICc(Log.CalfMod.Lag)


CalfMods.lag[[3]] <-
  Quad.CalfMod.Lag <-
  lmer(ZC13~Zcalves_lag+
      Zcalves.quad+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag)

summary(Quad.CalfMod.Lag)
AIcc_Calf.Quad.lag <- wiqid::AICc(Quad.CalfMod.Lag)

print(AIcc_Calf.Lin.Lag)
print(AIcc_Calf.Log.Lag)
print(AIcc_Calf.Quad.lag)



TLModels[[3]] <-
  Log.CalfMod.Lag 


```


### Lagged Moose Observation 

```{r}

MooseObsMods.Lag <- list()

MooseObsMods.Lag[[1]] <-
  Lin.MooseObsMod.Lag <- 
  lmer(ZC13~ Zobs_moose_lag+
  (1|BearID)+(1|Repro),
data = SI_Diet_Tlag) 

summary(Lin.MooseObsMod.Lag)
AIcc_MooseObs.Lin.Lag <- wiqid::AICc(Lin.MooseObsMod.Lag)

MooseObsMods.Lag[[2]] <-
  Log.MooseObsMod.Lag <- 
  lmer(ZC13~ Zobs_moose.ln_lag+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag) 
summary(Log.MooseObsMod.Lag)
AIcc_MooseObs.Log.Lag <- wiqid::AICc(Log.MooseObsMod.Lag)


MooseObsMods.Lag[[3]] <-
  Quad.MooseObsMod.Lag <-
  lmer(ZC13~Zobs_moose_lag+
      Zobs_moose.quad_lag+
      (1|BearID)+(1|Repro),
    data = SI_Diet_Tlag)

summary(Quad.MooseObsMod.Lag)
AIcc_MooseObs.Quad.Lag <- wiqid::AICc(Quad.MooseObsMod.Lag)

print(AIcc_MooseObs.Lin.Lag)
print(AIcc_MooseObs.Log.Lag)
print(AIcc_MooseObs.Quad.Lag)
summary(Log.MooseObsMod.Lag)

TLModels[[4]] <-  Quad.MooseObsMod.Lag

```



### Lagged Bilberry models


```{r}

BilbModels.Lag <- list()

BilbModels.Lag[[1]] <-LinBilbMod.Lag <-
  lmer(ZC13~ Zbilb_lag+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)

AIcc_Bilb.Lin.Lag <- wiqid::AICc(LinBilbMod.Lag)

BilbModels.Lag[[2]] <-QuadBilbMod.Lag <- 
  lmer(ZC13~ Zbilb_lag+Zbilb.quad_lag+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)

AIcc_Bilb.Quad.Lag <- wiqid::AICc(QuadBilbMod.Lag)


BilbModels.Lag[[3]] <-
  LogBilbMod.Lag <-
  lmer(ZC13~ Zbilb.ln_lag+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)


AIcc_Bilb.Log.Lag <- wiqid::AICc(LogBilbMod.Lag)

print(AIcc_Bilb.Lin.Lag)
print(AIcc_Bilb.Log.Lag)
print(AIcc_Bilb.Quad.Lag)

summary(LinBilbMod.Lag)


TLModels[[5]] <-  LinBilbMod.Lag


```


### Lagged age model


```{r}

TLModels[[6]] <-  
  AgeMod.Lag <- 
  lmer(ZC13~ Zage+
         (1|BearID)+(1|Repro),
       data = SI_Diet_Tlag)

summary(AgeMod.Lag)
AIcc_AgeLag <- wiqid::AICc(AgeMod.Lag)


```



## Model selection table

### year-year models

```{r}

CarbonModelNames <- c("Intercept",
                     "Year",
                     "Moose Harvest",
                     "Calf Observation",
                     "Moose Observation",
                     "Bilberry Index",
                     "Age",
                     "Calf + lnBilbberry")

##Generate and print AICc table
print(aictab(cand.set = CarbonModels,
             modnames = CarbonModelNames,
             sort = TRUE),
      digits = 4, #round to 4 digits after decimal point
      LL = TRUE #give log-likelihood 
      )

write.csv(aictab(cand.set = CarbonModels,
                 modnames = CarbonModelNames,
                 sort = TRUE,
                 second.ord=TRUE),
          file="Results\\CarbonModels.csv")

summary(CalfMod)
summary(BilbMod)
summary()



```


### time-lagged models

```{r}

TLModelNames <- c("Intercept",
                  "Lagged Moose Harvest",
                  "Lagged Calf Observation",
                  "Lagged Moose Observation",
                  "Lagged Bilberry Index",
                  "Age")

##Generate and print AICc table
print(aictab(cand.set = TLModels,
             modnames = TLModelNames,
             sort = TRUE),
      digits = 4, #round to 4 digits after decimal point
      LL = TRUE #give log-likelihood 
      )

write.csv(aictab(cand.set = TLModels,
                 modnames = TLModelNames,
                 sort = TRUE,
                 second.ord=TRUE),
          file="Results\\Carbon_TimeLagModels.csv")


ggplot(data = SI_Diet_Tlag, aes(age,C13.suess))+
  geom_jitter(width = 0.2,
              alpha=0.6,
              aes(color=Repro))+
  scale_color_viridis(option="B",
                      discrete = TRUE,
                      end=0.8)

```



## Compare the tim-lag with the year to year comparison

Because I originally ran the models on a slightly different dataset, they models arent comaprable. But I need to conclusively show that one model structure is better than the other. So I need to run the best-supported model without the lag on the same data that I ran the tim-lagged models on and determine whether there is stronger support for the time-lagged models than the year-year models. (I also need ot do the same for the nitrogen models)

For the year-year models, calf observations plus the bilberry index was the best model and moose observation had the most support for the time lag

```{r}

LogBilbCalfMod_lag <- lmer(ZC13~ Zbilb.ln+
                             Zcalves+
                             (1|BearID)+(1|Repro),
                           data = SI_Diet_Tlag)

AIcc_BilbCalf_lag <- AICc(LogBilbCalfMod_lag)
summary(LogBilbCalfMod_lag)

print(AIcc_BilbCalf_lag)

```



# Results

## Moose calf observations figure

```{r}

summary(LogBilbCalfMod)
Calf_TopMod_Carbon.df <- ggpredict(LogBilbCalfMod,
                        terms = "Zcalves")
Calf_TopMod_Carbon.df$Calves.og <- (Calf_TopMod_Carbon.df$x*sd(SI_Diet_Mharv$Calves))+
  mean(SI_Diet_Mharv$Calves)

Calf_TopMod_Carbon.df$Carb.og <- 
  (Calf_TopMod_Carbon.df$predicted*sd(SI_Diet_Mharv$C13.suess))+
  mean(SI_Diet_Mharv$C13.suess)

Calf_TopMod_Carbon.df$LCI <-
  (Calf_TopMod_Carbon.df$conf.low*sd(SI_Diet_Mharv$C13.suess))+
  mean(SI_Diet_Mharv$C13.suess)
Calf_TopMod_Carbon.df$UCI <- 
  (Calf_TopMod_Carbon.df$conf.high*sd(SI_Diet_Mharv$C13.suess))+
  mean(SI_Diet_Mharv$C13.suess)


```



```{r}

Calves_TopMode_Carbon.Plot <- 
  ggplot(data = Calf_TopMod_Carbon.df, aes(Calves.og,Carb.og))+
  geom_jitter(data = SI_Diet_Mharv,
              aes(Calves,C13.suess,
                  color=Year),
              size=2,
              alpha=0.4,
              width = 50)+
  geom_ribbon(aes(ymin=LCI, ymax=UCI),
              alpha=0.15)+
  geom_line(linewidth=0.9)+
  scale_y_continuous(expand = c(0.01,0.01))+
  scale_x_continuous(expand = c(0.01,0.01))+
  ylab(expression(paste(delta^13,"C (\u2030)",sep = "")))+
  xlab("Annual reported moose calf observations")+
  scale_color_viridis(option="C")+
  labs(color="Year")+
  add_phylopic(img = moose.img,
               x=4000, y=-22,
               ysize = 0.3,
               alpha=0.3)+
  add_phylopic(img = bilb.img,
               x=4000, y=-24,
               ysize = 0.3,
               alpha=0.3)

Calves_TopMode_Carbon.Plot

ggsave(plot = Calves_TopMode_Carbon.Plot,
       "Figures/Calves_TopMode_Carbon.png",
       width = 6.5, height = 6.5,
       units = "in",
       dpi = 800)

```


## Bilberry figure

```{r}

summary(LogBilbCalfMod)
Bilb_TopMod_Carbon.df <- ggpredict(LogBilbCalfMod,
                        terms = "Zbilb.ln",
                        back_transform = FALSE)

bilb.scratch1 <- Bilb_TopMod_Carbon.df$x*sd(SI_Diet_Mharv$Bilberry.LN)
bilb.scratch2 <- bilb.scratch1+mean(SI_Diet_Mharv$Bilberry.LN)
print(bilb.scratch2)
bilb.scratch3 <- exp(bilb.scratch2)
print(bilb.scratch3)

Bilb_TopMod_Carbon.df$Bilb.og <- bilb.scratch3

Bilb_TopMod_Carbon.df$Bilb.exp <- exp(Bilb_TopMod_Carbon.df$Bilb.og)

Bilb_TopMod_Carbon.df$Carb.og <- 
  (Bilb_TopMod_Carbon.df$predicted*sd(SI_Diet_Mharv$C13.suess))+
  mean(SI_Diet_Mharv$C13.suess)

Bilb_TopMod_Carbon.df$LCI <-
  (Bilb_TopMod_Carbon.df$conf.low*sd(SI_Diet_Mharv$C13.suess))+
  mean(SI_Diet_Mharv$C13.suess)
Bilb_TopMod_Carbon.df$UCI <- 
  (Bilb_TopMod_Carbon.df$conf.high*sd(SI_Diet_Mharv$C13.suess))+
  mean(SI_Diet_Mharv$C13.suess)


```



```{r}
library(rphylopic)


moose.img <- pick_phylopic(name = "Alces alces")
bilb.img <- pick_phylopic(name = "Vaccinium")

Bilb_TopMod_Carbon.plot <- 
  ggplot(data = Bilb_TopMod_Carbon.df, aes(Bilb.og,Carb.og))+
  geom_jitter(data = SI_Diet_Mharv,
              aes(Bilberry,C13.suess,
                  color=Year),
              size=2,
              alpha=0.4,
              width = 0.0051)+
  geom_ribbon(aes(ymin=LCI, ymax=UCI),
              alpha=0.15)+
  geom_line(linewidth=0.9)+
  scale_y_continuous(expand = c(0.01,0.01))+
  scale_x_continuous(expand = c(0.01,0.01))+
  ylab(expression(paste(delta^13,"C (\u2030)",sep = "")))+
  xlab("Annual bilberry production index")+
  scale_color_viridis(option="C")+
  labs(color="Year")+
  add_phylopic(img = moose.img,
               x=0.025, y=-22,
               ysize = 0.3,
               alpha=0.3)+
  add_phylopic(img = bilb.img,
               x=0.025, y=-24,
               ysize = 0.3,
               alpha=0.3)

Bilb_TopMod_Carbon.plot

ggsave(plot = Bilb_TopMod_Carbon.plot,
       "Figures/Bilb_TopMod_Carbon.png",
       width = 6.5, height = 6.5,
       units = "in",
       dpi = 800)

```



## Both figures in one plot


```{r}

Bilb_TopMod_Carbon.plot2 <- Bilb_TopMod_Carbon.plot+
  theme(legend.position = "none",
        axis.title.y = element_blank())+
  geom_text(label="B",
            y= -21.7, x=1,
            size=4)
Bilb_TopMod_Carbon.plot2

Calves_TopMode_Carbon.Plot2 <- Calves_TopMode_Carbon.Plot+
  theme(legend.position = "left",
        axis.text.y = element_blank())+
  geom_text(label="A",
            y= -21.7, x=14000,
            size=4)
Calves_TopMode_Carbon.Plot2


CarbonFig <- 
  grid.arrange(Calves_TopMode_Carbon.Plot2,
               Bilb_TopMod_Carbon.plot2,
               ncol=2,
               nrow=1)

ggsave(plot = CarbonFig,
       "Figures/TopModel_Carbon.png",
       width=10.5, height = 6,
       units = "in",
       dpi=800)

```



```{r}


ggplot(data = SI_Diet_Mharv, aes(Bilberry, Calves))+
  geom_point()

```

